### 2016-04-11 document/manuscript-plos.tex
last update/compile before submission
Update manuscript-plos.tex
I have removed the reviewers from the acknowledgments, as requested by PLOS Comp. Biology.

The authors would like to thank C. Titus Brown, Chris Fields and an
anonymous reviewer for their helpful comments in improving the
manuscript. We would also like to thank C. Titus Brown from
advertising contributions to the manuscript on social media, leading
to further contributions and improvements. We also thank Peter Cock
(peterjc) for helpful suggestion contributed directly though GitHub.

>>>>

The authors would like to thank C. Titus Brown for mentioning
the manuscript on social media, leading to additional contributions
and further improvements. We also thank Peter Cock (peterjc) for
helpful suggestion contributed directly though GitHub.
